---
title: "ICU report"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(data.table) ## For the fread function
library(lubridate)

source("sepsis_monitor_functions.R")
```


library(tictoc)

tic()
test1=makeSepsisDataset(n=50,read_fn = "fread")
print(paste0("-----n=50,function=fdread"))
toc()

tic()
test1=makeSepsisDataset(n=50,read_fn = "read_delim")
print(paste0("-----n=50,function=read_delim"))
toc()

tic()
test1=makeSepsisDataset(n=100,read_fn = "fread")
print(paste0("-----n=100,function=fdread"))
toc()

tic()
test1=makeSepsisDataset(n=100,read_fn = "read_delim")
print(paste0("-----n=100,function=read_delim"))
toc()

tic()
test1=makeSepsisDataset(n=500,read_fn = "fread")
print(paste0("-----n=500,function=fdread"))


```{r}
library(googledrive)

df <- makeSepsisDataset()

# We have to write the file to disk first, then upload it
df %>% write_csv("sepsis_data_temp.csv")

# Uploading happens here
sepsis_file <- drive_put(media = "sepsis_data_temp.csv", 
          path = "https://drive.google.com/drive/folders/11IKA3vU7zxrzMB8ftvh5OZ7-x93-R-gi",
          name = "sepsis_data.csv")

# Set the file permissions so anyone can download this file.
sepsis_file %>% drive_share_anyone()

```

```{r}
### Date and Time: `r Sys.time()`
drive_deauth()
file_link <- "https://drive.google.com/file/d/1-ffRV8NmmnPN25PFa_ziGOSG9khU-Svc/view?usp=sharing"

## All data up until now
new_data <- updateData(file_link)

## Include only most recent data
most_recent_data <- new_data %>%
  group_by(PatientID) %>%
  filter(obsTime == max(obsTime))

# A table listing the patients who currently have sepsis (if any), along with their most recent heart rate, temperature, and respiratory rate
sepsis_patients <- most_recent_data %>%
  filter(SepsisLabel == 1) %>%
  select(PatientID, HR, Temp, Resp)
sepsis_patients


```

```{r}
#Plots for all patients who have sepsis (if any) that show the complete history of their heart rate, temperature, and respiratory rate during their time in the ICU.
library(cowplot)
sepsis_patients <- most_recent_data %>%
  filter(SepsisLabel == 1) %>%
  select(PatientID, HR, Temp, Resp)

### "001118" "004939" "007540" "007540" Temperature: NA
sepsis_patients_ids <- unique(sepsis_patients$PatientID)
patient_plots <- list()
for (patient in sepsis_patients_ids) { 
  patient_data <- new_data %>%
    filter(PatientID == patient) %>%
    select(ICULOS, HR, Temp, Resp)
  
  plot_1 <- ggplot(patient_data, aes(x = ICULOS, y = HR)) +
    geom_line() +
    ggtitle(paste0("Heart Rate for Patient ", patient)) +
    theme_minimal() +
    xlab("Duration of ICU stay in hours") +
    ylab("Heart Rate")
  
  plot_2 <- ggplot(patient_data, aes(x = ICULOS, y = Temp)) +
    geom_line() +
    ggtitle(paste0("Temperature for Patient ", patient)) +
    theme_minimal() +
    xlab("Duration of ICU stay in hours") +
    ylab("Temperature")
  
  plot_3 <- ggplot(patient_data, aes(x = ICULOS, y = Resp)) +
    geom_line() +
    ggtitle(paste0("Respiratory Rate for Patient ", patient)) +
    theme_minimal() +
    xlab("Duration of ICU stay in hours") +
    ylab("Respiratory Rate")
  
  patient_plots[[patient]] <- list(plot_1, plot_2, plot_3)
}

plot_grid(plotlist = unlist(patient_plots, recursive = FALSE),
          ncol = 3, labels = "AUTO", label_size = 12)
```

```{r}
#A table showing the change in heart rate, temperature, and respiratory rate between the last two measurements for all patients
changing <- new_data %>%
  group_by(PatientID) %>%
  arrange(PatientID, ICULOS) %>%
  slice_tail(n = 2) %>%
  mutate(across(c(HR, Temp, Resp), list(change = ~ . - lag(.)))) %>%
  filter(!is.na(HR_change) | !is.na(Temp_change) | !is.na(Resp_change)) %>%
  select(PatientID, HR_change, Temp_change, Resp_change) %>%
  pivot_longer(cols = c(HR_change, Temp_change, Resp_change), names_to = "variable", values_to = "change") %>%
  mutate(change_direction = case_when(change > 0 ~ "increased",
                                      change < 0 ~ "decreased",
                                      TRUE ~ "same"))
changing
```




